A SIMPLE PRIMAL-DUAL ALGORITHM FOR COMPUTING APPROXIMATE NASH-EQUAILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION

### 2015-09-28 paper.tex
glitches + fixups + ENHs

%% squeezing
\linespread{0.85}
\usepackage[compact]{titlesec}
%\titlespacing{\section}{0pt}{2ex}{1ex}
\titlespacing{\subsection}{0pt}{1ex}{0ex}
\titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}

@@

% Title.
% ------
\title{A SIMPLE AND EFFICIENT ALGORITHM FOR COMPUTING APPROXIMATE
  NASH-EQUAILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION}

%
% Single address.
% ---------------
\name{Elvis Dohmatob}
\address{Parietal Team, INRIA, Universit\'e de Paris-Saclay}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
 %% {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
 %%        {School A-B\\
 %%        Department A-B\\
 %%        Address A-B}
 %% {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
 %%        while at ...}}
 %%        {School C-D\\
 %%        Department C-D\\
 %%        Address C-D}
%
% More than two addresses
% -----------------------
% \name{Author Name$^{\star \dagger}$ \qquad Author Name$^{\star}$ \qquad Author Name$^{\dagger}$}
%
% \address{$^{\star}$ Affiliation Number One \\
%     $^{\dagger}$}Affiliation Number Two
%

@@

\maketitle
\begin{abstract}
We present a simple primal-dual algorithm for
  computing approximate Nash-equilibria in two-person zero-sum
  sequential games with  incomplete information and perfect recall
  (like Texas Hold'em poker). Our algorithm only performs basic
  iterations (i.e matvec multiplications, clipping, etc., and no calls
  to external first-order oracles, no matrix inversions, etc.)
  and is applicable to a broad class of two-person zero-sum games
  including simultaneous games and sequential games with incomplete
  information and perfect recall. The applicability to the latter kind
  of games is thanks to the sequence-form representation
  which allows us to encode any such game
  as a matrix game with convex polytopial profiles. We prove that
  the number of iterations needed to produce a Nash-equilibrium with a
  given precision is inversely proportional to the
  precision. By way of demonstration, we also present experimental
  results on simulated and real games (Kuhn poker).
\end{abstract}

\begin{keywords} algorithmic-game theory, sequential games,
incomplete information, perfect recall, approximate Nash-equilibrium
\end{keywords}

\section{Introduction}
\label{sec:intro}
A game-theoretic approach to playing games strategically optimally
consists of computing Nash-equilibria (in fact, approximations thereof)
offline, and playing one's part (an optimal \textit{behavioral}
strategy) of the equilibrium online. This
technique is the driving-force behind solution concepts like CFR
\cite{zinkevich2008regret,lanctot2009monte,Bowling09012015},
$\text{CFR}^{+}$ \cite{tammelin14} and other variants, which
have recently had profound success in poker. However, solving games
for equilibria remains a mathematical and computational challenge,
especially in sequential games with imperfect information. This paper
proposes a simple and efficient algorithm for solving for such
equilibria approximately, in a sense which will be made clear shortly.

\subsection{Notation and terminology}
Let $m$ and $n$ be positive integers. Given two
vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
$\langle z, w\rangle := \sum_{j}z_jw_j$. The components of $z$ will be
denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
not $1$). $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ }
z \geq 0\}$ is the nonnegative $n$th \textit{orthant}.
The notation ``$z \ge 0$'' means that all the components of
$z$ are nonnegative.
$\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| :=
\sqrt{\langle z, z\rangle}$. $(z)_+:=\text{max}(0, z) \in
\mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
function. The $n$-simplex denoted $\Delta_n$, is defined by $\Delta_n
:= \{z \in \mathbb{R}^n_+|\sum_j z_j = 1\}$.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

Let us introduce some basic but powerful modern convex-analytical
notions which will be essential in the sequel. Given a subset $C$ of
$\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined
by $i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise}$.
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). For example, we will write $i_{z \ge 0}$ for
$i_{\mathbb{R}^n_+}(z)$, etc. Let $f : \mathbb{R}^n \rightarrow
(-\infty, +\infty]$ be a
  convex function. The \textit{orthogonal projector} onto $C$, is the
  ``closest-point function'' $\proj_C: \mathbb{R}^n \rightarrow C, x
  \mapsto \underset{z \in
      C}{\text{argmin }}\frac{1}{2}\|z-x\|^2$.
The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
$dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$.
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subdifferential} of $f$ at a point $x \in \mathbb{R}^n$ is
defined by
$\partial f(x) := \{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z -
x\rangle, \forall z \in \mathbb{R}^n\}$.
%% Each element of $\partial f(x)$ is called a \textit{subgradient} of $f$
%% at $x$. Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
%% in case $f$ is differentiable at $x$.
If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by $\prox_f(x): = \underset{z \in
  \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z)$.
%% For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
%% $\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
%% operators generalize orthogonal projectors. For example
%% $\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
%% (z)_+$. One also has the useful characterization
%% \begin{eqnarray}
%%   p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
%% \end{eqnarray}
%% Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
%% should) be thought of as performing an \textit{implicit} gradient step
%% of size $\gamma$.

@@

\subsection{Statement of the problem}

The sequence-form representation for two-person zero-sum games with
incomplete information was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium} where it was
established that for such games, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash-equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP (Linear Convex Program)
\begin{equation}
  \begin{aligned}
    \underset{(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1}}{\text{minimize }}\langle e_1,
    p\rangle \hspace{.5em}\text{
       subject to: } &y \ge 0, E_2y = e_2,\\
    &-Ay + E_1^Tp \geq 0,
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

Note that the LCPs above have the equivalent saddle point formulation
\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle,
  \label{eq:gilpin}
\end{equation}
where the \textit{convex polytope} (by which we mean a bounded convex
polyhedron)
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\} \subseteq
  [0, 1]^{n_k}
\label{eq:polytope}
\end{equation}
is identified with the strategy profile of player $k$ in the
sequence-form representation. At a feasible point $(y, p, x, q)$ for
the LCPs, the \textit{primal-dual gap} $\tilde{G}(y, p, x, q)$ is
given by\footnote{The first inequality being due to \textit{weak
    duality}.}
\begin{eqnarray}
  \begin{split}
  0 &\le \tilde{G}(y, p, x, q) := \langle e_1, p\rangle - (-\langle
  e_2, q\rangle) = \langle e_1, p\rangle + \langle
  e_2, q\rangle\\
  &= G(x, y) := \mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
(u,v) \in Q_1 \times Q_2\}.
\end{split}
  \label{eq:dgap}
\end{eqnarray}

In \eqref{eq:dgap}, the quantity $G(x, y)$ is nothing but the primal-dual
gap for the equivalent saddle point problem \eqref{eq:gilpin}.
It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
equilibrium for the game)  if and only if there exist vectors $p$ and
$q$ such that
\begin{equation}
\begin{split}
\hspace{.25em} -Ay + E_1^Tp \ge 0, &\hspace{.5em}A^Tx + E_2^Tq \ge
0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0,\\
&\langle y, A^Tx  + E_2^Tq\rangle = 0.
\end{split}
\label{eq:feasibility}
\end{equation}

Moreover, at equilibria, \textit{strong duality} holds and the value
of the game equals $p_0 = -q_0$, i.e the primal-dual gap
$\tilde{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at
equilibria.

Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
is impossible in practice (indeed, this system of problems is NP-hard
\cite{koller1992complexity}) and such a precision doesn't have any
fundamental practical advantage. Instead, it is customary compute
``approximate'' Nash-equilibria. A popular notion of approximate
equilibria is the following:

\begin{definition}[\textbf{Nash $\epsilon$-equilibria}]
Given $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
a pair $(x^*, y^*)$ of realization plans such that there exists dual
vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} such that the primal-dual gap at $(y^*, p^*, x^*, q^*)$
doesn't exceed $\epsilon$. That is,

\begin{remark}
It should be noted
that any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
  game with payoff matrix $A$, for which each player's strategy
profile is a simplex; this simplex can be written in the form
\eqref{eq:polytope} by taking $E_k := (1, 1, ..., 1) \in
\mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
matrix game on simplexes can be seen as a sequential game.  Thus the
results presented in this manuscript can be trivially applied such
games in particular. Here, the polytopial $Q_k$
defined in \eqref{eq:polytope} reduce to simplexes $\Delta_{n_k}$,
and the primal-dual gap function $G(x,y)$ writes
\begin{eqnarray}
\begin{split}
G(x, y) &=
\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
\Delta_{n_1} \times \Delta_{n_2}\}\\
&= \underset{0 \le i <
  n_1}{\text{max }}(Ay)_i - \underset{0 \le j < n_2}{\text{min
}}(A^Tx)_j.
\end{split}
\label{eq:mg_pd}
\end{eqnarray}
\end{remark}

\subsection{Quick sketch of our contribution}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the orthogonal projections $\proj_{Q_k}$ is very difficult
In fact, such sub-problems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}. Also,
the primal-dual gap might explode even at points arbitrarily close to
the set of feasible points, leaving the algorithm with no indication
whatsoever, on whether progress is being made or not. So need to way to
\begin{itemize}
\item[(1)] avoid having to compute the projections $\proj_{Q_k}$,
\item[(2)] have control over how far we are from the set of
  equilibria and avoid infinite (and thus non-informative) primal-dual
  gaps.
\end{itemize}

Developing on an alternative notion of approximate equilibria (see
Definition \ref{thm:cool_notion})
homologous to that presented in Definition \ref{thm:approx_nash}, we
device a primal-dual algorithm that (Algorithm \ref{Tab:algo}) for
computing approximate Nash-equilibria in sequential two-person
zero-sum games with incomplete information and perfect recall, and
which satisfies the above crucial requirements (1)--(2). We also
prove (Theorem \ref{thm:pd}) that --in an ergodic / Ces\`ario sense-- the number of
iterations required by the algorithm to produce an approximation
equilibrium to a precision $\epsilon$ is $\mathcal{O}(1/\epsilon)$,
with explicit values for the constants involved this worst-case cost.
These contributions will be elaborated in section \ref{sec:gsp}.
%%  The source of approximation in our scheme
%% is that we explicitly control how close we are to the feasible set
%% $Q_1 \times Q_2$.

>>>>

%% squeezing
\linespread{0.845}
\usepackage[compact]{titlesec}
%\titlespacing{\section}{0pt}{2ex}{1ex}
\titlespacing{\subsection}{0pt}{1ex}{0ex}
\titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}

@@

% Title.
% ------
\title{A SIMPLE PRIMAL-DUAL ALGORITHM FOR COMPUTING APPROXIMATE
  NASH-EQUAILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION}

%
% Single address.
% ---------------
\name{Elvis Dohmatob}
\address{Parietal Team, INRIA / CEA, Universit\'e Paris-Saclay}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
 %% {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
 %%        {School A-B\\
 %%        Department A-B\\
 %%        Address A-B}
 %% {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
 %%        while at ...}}
 %%        {School C-D\\
 %%        Department C-D\\
 %%        Address C-D}
%
% More than two addresses
% -----------------------
% \name{Author Name$^{\star \dagger}$ \qquad Author Name$^{\star}$ \qquad Author Name$^{\dagger}$}
%
% \address{$^{\star}$ Affiliation Number One \\
%     $^{\dagger}$}Affiliation Number Two
%

@@

\maketitle
\begin{abstract}
We present a simple primal-dual algorithm for computing approximate
Nash-equilibria in two-person zero-sum sequential games with
incomplete information and perfect recall (like Texas Hold'em
Poker). Our algorithm is numerically stable, performs basic
iterations (i.e matvec multiplications, clipping, etc., and no calls
to external first-order oracles, no matrix inversions, etc.) and is
applicable to a broad class of two-person zero-sum games including
simultaneous games and sequential games with incomplete information
and perfect recall. The
applicability to the latter kind of games is thanks to the
sequence-form representation which allows us to encode any such game
as a matrix game with convex polytopial strategy profiles. We prove
that the number of iterations needed to produce a Nash-equilibrium
with a given precision is inversely proportional to the precision. As
proof-of-concept, we present experimental results on matrix games
on simplexes and Kuhn Poker.
\end{abstract}

\begin{keywords} Nash-equilibrium, sequential games,
  incomplete information, perfect recall, convex optimization
\end{keywords}

\section{Introduction}
\label{sec:intro}
A game-theoretic approach to playing games strategically optimally
consists of computing Nash-equilibria (in fact, approximations thereof)
offline, and playing one's part (an optimal \textit{behavioral}
strategy) of the equilibrium online. This
technique is the driving-force behind solution concepts like CFR
\cite{zinkevich2008regret,lanctot2009monte,Bowling09012015},
$\text{CFR}^{+}$ \cite{tammelin14} and other variants, which
have recently had profound success in Poker. However, solving games
for equilibria remains a mathematical and computational challenge,
especially in sequential games with imperfect information. In this
paper, we propose a simple primal-dual algorithm for solving for such
equilibria approximately (in a sense to be made precise in Definition
\ref{thm:cool_notion} below).

\subsection{Statement of the problem}
The sequence-form representation for two-person zero-sum games with
incomplete information was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium} where it was
established that for such games, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash-equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP (Linear Convex Program)
\begin{equation}
  \begin{aligned}
    \underset{(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1}}{\text{minimize }}\langle e_1,
    p\rangle \hspace{.5em}\text{
       subject to: } &y \ge 0, E_2y = e_2,\\
    &-Ay + E_1^Tp \geq 0,
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

The LCPs above have the equivalent saddle-point formulation
\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle,
  \label{eq:gilpin}
\end{equation}
where the \textit{convex polytope} (by which we mean a bounded convex
polyhedron)
\begin{equation}
  Q_k := \{z \ge 0 |\text{ }E_kz = e_k\} \subseteq
  [0, 1]^{n_k}
\label{eq:polytope}
\end{equation}
is identified with the strategy profile of player $k$ in the
sequence-form representation. At a feasible point $(y, p, x, q)$ for
the LCPs, the \textit{primal-dual gap} $\tilde{G}(y, p, x, q)$ is
given by\footnote{The first inequality being due to \textit{weak
    duality}.}
\begin{eqnarray}
  \begin{split}
  0 &\le \tilde{G}(y, p, x, q) := \langle e_1, p\rangle - (-\langle
  e_2, q\rangle) = \langle e_1, p\rangle + \langle
  e_2, q\rangle\\
  &= G(x, y) := \mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
(u,v) \in Q_1 \times Q_2\}.
\end{split}
  \label{eq:dgap}
\end{eqnarray}

In \eqref{eq:dgap}, the quantity $G(x, y)$ is nothing but the primal-dual
gap for the equivalent saddle-point problem \eqref{eq:gilpin}.
It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
equilibrium for the game)  if and only if there exist vectors $p$ and
$q$ such that
\begin{equation}
\begin{split}
\hspace{.25em} -Ay + E_1^Tp \ge 0, &\hspace{.5em}A^Tx + E_2^Tq \ge
0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0,\\
&\langle y, A^Tx  + E_2^Tq\rangle = 0.
\end{split}
\label{eq:feasibility}
\end{equation}
Moreover, at equilibria, \textit{strong duality} holds and the value
of the game equals $p_0 = -q_0$, i.e the primal-dual gap
$\tilde{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at
equilibria.%%  Solving the LCPs \eqref{eq:primal_pb} and
%% \eqref{eq:dual_pb} exactly is very practice
%% \cite{koller1992complexity}) and such a precision doesn't have any
%% fundamental practical advantage. Instead, it is customary compute
%% ``approximate'' Nash-equilibria.%%  A now introduce a popular notion of
%% %% approximate Nash-equilibria:

\begin{definition}[\textbf{Nash $\epsilon$-equilibria}]
Given $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
a pair $(x^*, y^*)$ of realization plans for which there exists dual
vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} such that the primal-dual gap at $(y^*, p^*, x^*, q^*)$
doesn't exceed $\epsilon$. That is,

\subsection{Notation and terminology}
\paragraph*{General.} Let $m$ and $n$ be positive integers.
The components of a vector $z \in \mathbb{R}^n$ will be
denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
not $1$). $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ }
z \geq 0\}$ is the nonnegative $n$th \textit{orthant}.
The notation ``$z \ge 0$'' means that all the components of
$z$ are nonnegative.
$\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| :=
\sqrt{\langle z, z\rangle}$. $(z)_+:=\text{max}(0, z) \in
\mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
function. The $n$-simplex denoted $\Delta_n$, is defined by $\Delta_n
:= \{z \in \mathbb{R}^n_+|\sum_j z_j = 1\}$.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

\paragraph*{Convex analysis.} Let us introduce some basic but powerful
modern convex-analytical
notions which will be essential in the sequel. Given a subset $C$ of
$\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined
by $i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise}$.
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). For example, we will write $i_{z \ge 0}$ for
$i_{\mathbb{R}^n_+}(z)$, etc.  The \textit{orthogonal projector} onto $C$, is the
``closest-point'' map $\proj_C: \mathbb{R}^n \rightarrow C, x
  \mapsto \underset{z \in
      C}{\text{argmin }}\frac{1}{2}\|z-x\|^2$.
Let $f : \mathbb{R}^n \rightarrow
(-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
$dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$.
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subdifferential} of $f$ at a point $x \in \mathbb{R}^n$ is
defined by
$\partial f(x) := \{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z -
x\rangle, \forall z \in \mathbb{R}^n\}$.
%% Each element of $\partial f(x)$ is called a \textit{subgradient} of $f$
%% at $x$. Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
%% in case $f$ is differentiable at $x$.
If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by $\prox_f(x): = \underset{z \in
  \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z)$.
%% For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
%% $\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
%% operators generalize orthogonal projectors. For example
%% $\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
%% (z)_+$. One also has the useful characterization
%% \begin{eqnarray}
%%   p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
%% \end{eqnarray}
%% Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
%% should) be thought of as performing an \textit{implicit} gradient step
%% of size $\gamma$.

@@

\subsection{A remark concerning matrix games on simplexes.} It should
be noted
that any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
  game with payoff matrix $A$, for which each player's strategy
profile is a simplex; this simplex can be written in the form
\eqref{eq:polytope} by taking $E_k := (1, 1, ..., 1) \in
\mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
matrix game on simplexes can be seen as a sequential game, and so the
results presented in this manuscript can be trivially applied such
games in particular. For this special sub-class of sequential games,
the primal-dual gap function $G(x,y)$ writes
\begin{eqnarray}
\begin{split}
G(x, y) &=
\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
\Delta_{n_1} \times \Delta_{n_2}\}\\
&= \underset{0 \le i <
  n_1}{\text{max }}(Ay)_i - \underset{0 \le j < n_2}{\text{min
}}(A^Tx)_j.
\end{split}
\label{eq:mg_pd}
\end{eqnarray}

\subsection{Quick sketch of our contribution}
%% One cannot directly attack the LCPs
%% \eqref{eq:primal_pb} and
%% \eqref{eq:dual_pb} via a traditional primal-dual algorithm
%% (for example \cite{chambolle2010,chambolle2014ergodic}) because
%% computing the orthogonal projections $\proj_{Q_k}$ is very difficult
%% In fact, such sub-problems would have to be solved
%% iteratively\footnote{An ``exception to the rule'' is the case where
%%   the $Q_k's$ are simplexes, so that the projections can be computed
%%   exactly using \cite{duchi2008efficient}.}.

Developing on an alternative notion of approximate equilibria (see
Definition \ref{thm:cool_notion})
homologous to that presented in Definition \ref{thm:approx_nash}, we
device a simple numerically stable primal-dual algorithm that
(Algorithm \ref{Tab:algo}) for computing approximate Nash-equilibria
in sequential two-person zero-sum games with incomplete information and
perfect recall. On, each iteration, the only operations performed by
our algorithm are of the form $A^Tx$, $Ay$, $E_1^Tp$, $E_2^Tq$, and
$(x)_+$. We also prove (Theorem \ref{thm:pd}) that --in an ergodic /
Ces\`ario sense-- the number of iterations required by the algorithm
to produce an approximation equilibrium to a precision $\epsilon$ is
$\mathcal{O}(1/\epsilon)$, with explicit values for the constants
involved this worst-case cost.
%% The source of approximation in our scheme
%% is that we explicitly control how close we are to the feasible set
%% $Q_1 \times Q_2$.
% These contributions will be elaborated in section \ref{sec:gsp}.

\section{Relation to prior work}
\label{sec:related_work}
We now present a selection of algorithms that is representative of the
efforts that have been made in the literature to compute Nash
$\epsilon$-equilibria for two-person zero-sum games with incomplete
information like Texas Hold'em Poker, etc.
First and foremost, let us note that for the class of games considered
here (sequential games with incomplete information), the LCPs
\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
than what state-of-the-art LCP and interior-point solvers can
handle (see for example \cite{hoda2010smoothing,gilpinfirst}).

\subsection{Regret minimization}
CFR (CounterFactual Regret minimization) \cite{zinkevich2008regret},
Monte Carlo CFR \cite{lanctot2009monte}, and CFR+
\cite{Bowling09012015}, by their large popularity, have become the
definitive state-of-the-art, and are particularly useful in
many-player games, since convex-analytical methods cannot help much in
such games. Also, they can be shown to converge to a Nash-equilibrium
provided each player uses a CFR scheme to play the game
\cite{zinkevich2008regret}, but generally enjoy a much weaker
convergence theory. For example, \cite{lanctot2009monte} showed that
such scheme have a running time of $\mathcal{O}(1/\epsilon^2)$ to
produce a Nash $\epsilon$-equilibrium.

\subsection{First-order methods}
In \cite{hoda2010smoothing}, a nested iterative procedure using the
Excessive Gap Technique (EGT) \cite{nesterov2005excessive} (EGT and
precursors are well-known to the signal-processing community
\cite{NESTA}) was used
to solve the equilibrium problem \eqref{eq:gilpin}.
The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
(which derives from the general EGT theory) for the outer-most
iteration loop.
\cite{gilpinfirst} proposed a modified version of the techniques in
\cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
\delta\right) \log \left(1 / \epsilon\right)\right)$ convergence rate in
terms of the number of calls made to a first-order oracle. Here
$\delta = \delta(A, E_1, E_2, e_1, e_2) > 0$ is a certain
\textit{condition number} for the game. The crux of their technique was to
observe that \eqref{eq:gilpin} can further be written a the minimization of
the primal-dual gap function $G(x, y)$ (defined in \eqref{eq:dgap})
for the game\footnote{The minimizers of $G$ are precisely the
  equilibria of the game.}, viz
\begin{eqnarray}
\mathrm{minimize}\{G(x,y)|(x,y) \in Q_1 \times Q_2\},
\end{eqnarray}
and then show there exists a scalar
$\delta > 0$ such that for any pair of realization plans $(x, y) \in Q_1 \times Q_2$,
\begin{eqnarray}
\text{``distance between }(x, y)\text{ and the set of
equilibria'' } \le G(x, y)/\delta.
\end{eqnarray}
Their
algorithm is then derived by iteratively applying Nesterov smoothing \cite{nesterov2005a}
with a geometrically decreasing sequence of tolerance levels
$\epsilon_{n+1} = \epsilon_n / \gamma$ (with $\gamma > 1$)  $G$. It
should be noted however that
\begin{itemize}
\item[--] The constant $\delta > 0$ can be arbitrarily small, and so
  the factor $\|A\| / \delta$ in the $\mathcal{O}\left(\left(\|A\| /
\delta\right) \log\left(1 / \epsilon\right)\right)$ convergence rate can
be arbitrarily large for ill-conditioned games.
\item[--] The reported linear convergence rate is not in terms of
  basic operations (addition, multiplication, matvec, clipping, etc.),
  but in terms of the number of calls to a first-order oracle. Most
  notably, the complicated projections $\proj_{Q_k}$ are applied at
  each iteration.%%  Of
  %% course, the existence of a linear algorithm for solving
  %% \eqref{eq:gilpin} is improbable, as the usual strong-convexity
  %% conditions are absent.
\end{itemize}
Recently, \cite{kroer2015} proposed accelerations to first-order
methods for computing Nash-equilibria (including those just
discussed), by an appropriate choice of the underlying \textit{Bregman
distance} and the \textit{distance generating function} (essential
ingredients in EGT-type algorithms). These modifications provably
gain a constant factor in the worst-case convergence rate of the
resulting algorithm. %, compared to \textit{vanilla} implementations.

\subsection{Primal-dual algorithms}
The primal-dual algorithm first developed in \cite{chambolle2010}, was
proposed in \cite{chambolle2014ergodic} as a way of solving matrix
games on simplexes. Notably, such matrix games on
simplexes are considerably simpler than the games considered
here. Indeed, the authors in \cite{chambolle2014ergodic} used the fact
that computing the orthogonal projection of a point onto a simplex can
be done in linear time as in \cite{duchi2008efficient}. In contrast,
no such efficient algorithm is known nor is likely to exist, for the
polytopes $Q_k$ defined in \eqref{eq:polytope}. %% , the strategy
%% profiles for players in %% the games considered here.
That notwithstanding, such projections can still be done iteratively
using for example, the algorithm in proposition 4.2 of
\cite{combettes2010dualization} or the algorithms developed in
\cite{tran2015splitting}. Unfortunately, as with any nested iterative
scheme, one would have to solve this sub-problem with finer and finer
precision, rendering the overall solver impractical.

 Also, the primal-dual gap might explode even at points arbitrarily
 close to the set of feasible points, leaving the algorithm with no
 indication whatsoever, on whether progress is being made or not. So,
 we need a way to \textit{(1)} avoid having to compute the projections
$\proj_{Q_k}$, and \textit{(2)} have control over how far we are from
the set of equilibria and avoid infinite (and thus non-informative)
primal-dual gaps. Amongst other amendments, this issue was addressed
in \cite{he2013accelerating}.
